### 2013-08-13 Tex/chapters/model.tex
Klarere Formulierung
Reduktion von disordered auf standrd etwas erklärt

@@

    site \(i\).\\
    In this thesis \(\tilde{H}_i=0 \ \forall i\). The most important
    modification is, that the sites of the square lattice are displaced.

@@

    identified with edge weights. The weight of an edge \(E_{ij}\) is
    \(J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidean

@@

    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
    for which exists an analytic solution \cite{Onsager1944} for the

>>>>

    For the standard Ising model \(J_{ij}=1 \forall i,j\) applies.

@@

    site \(i\). For the standard Ising model \(\tilde{H}_i=0 \ \forall i\)
    applies.\\
    The most important modification of the standard Ising modell in this
    thesis is, that the sites of the square lattice are displaced.

@@

    identified with edge weights. The weight of an edge \(E_{ij} =
    J_{ij} = \exp (\alpha (1-d_{ij}))\) where \(d_{ij}\) is the Euclidean

@@

    Note that for \(\sigma = 0\) all \(d_{ij} = 1\) and therefore all
    \(J_{ij} = 1\), so that the disordered Ising model is reduced to the
    standard Ising model. For this exists an analytic solution \cite{Onsager1944} for the
